CAD and Routing Architecture for Interposer-Based Multi-FPGA Systems

### 2014-12-08 doc/journal/fpgapaperfinal/FPGAPaper/fpga2014paper.tex
fixing the graph that had a duplicate label as an earlier graph
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4522 8e3573b8-cf2c-4f14-ef6d-137439e28b8b
Adding incomplete draft of partitioning section.
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4523 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{epstopdf}
\usepackage{enumitem}
\usepackage{cite}
\usepackage[cmex10]{amsmath}

@@

The optimizations also help the placer to place related entities on the same die to reduce the number of inter-die signal crossings and hence increase circuit speed. At 80\% wires cut, the placer optimizations result in 8.4\% higher circuit speed.
\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{placer_opt_fmax.eps}
\caption{Impact of placer optimizations on circuit speed.}
\label{fig:comparison_minW}
\end{figure}

@@

%---------------------------------------------------------------
%---------------------------------------------------------------
%---------------------------------------------------------------
\section{Adding Partitioning to the CAD Flow}
\label{sec:CADflow}
TODO: Javeed

@@

%   - Impact of # of cutlines
\subsection{Impact of Number of Dice}
\label{num_dice_impact}
TODO: Javeed\\
To examine the impact of the number of die used to construct an interposer-based FPGA, we varied the number of cuts from 1 to 3 (which varies the number of die from 2 to 4).  In these experiments, the \textit{delay increase} was kept constant at $1ns$.

>>>>

\usepackage[cmex10]{amsmath}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{subfigure}
\usepackage{epstopdf}
\usepackage{enumitem}
\usepackage{cite}

\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}

@@

The optimizations also help the placer to place related entities on the same die to reduce the number of inter-die signal crossings and hence increase circuit speed. At 80\% wires cut, the placer optimizations result in 8.4\% higher circuit speed.
\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{placer_opt_fmax.eps}
\caption{Impact of placer optimizations on circuit speed.}
\label{fig:comparison_fmax}
\end{figure}

@@

%---------------------------------------------------------------
%---------------------------------------------------------------
%---------------------------------------------------------------
\input{partitioning.tex}

@@

%   - Impact of # of cutlines
\subsection{Impact of Number of Dice}
\label{num_dice_impact}
TODO: Javeed
To examine the impact of the number of die used to construct an interposer-based FPGA, we varied the number of cuts from 1 to 3 (which varies the number of die from 2 to 4).  In these experiments, the \textit{delay increase} was kept constant at $1ns$.
